A survey of HTTP caching options on the open Semantic Web

### 2015-01-19 sanity/paper1.tex
Colors iin the mosaic plots; reordered table
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1017 43ef1190-90fd-4dd7-a769-d0121f02b80e

\begin{figure}[ht]
  \centerline{%
    \includegraphics[width=.9\textwidth]{hardtable.pdf}}
  \caption{Mosaic Plot. Divided by type of resource on the vertical
    axis and by the same bins as in Figure~\ref{fig:hardall} on the
    horizontal axis. }
  \label{fig:hardtable}
\end{figure}

@@

\begin{figure}[hb!]
  \centerline{%
    \includegraphics[width=.9\textwidth]{heuristictable.pdf}}
  \caption{Mosaic Plot. Divided by type of resource on the vertical
    axis and by the same bins as in Figure~\ref{fig:hardall} on the
    horizontal axis. }
  \label{fig:heuristictable}
\end{figure}

>>>>

\begin{figure}[ht]
  \centerline{%
    \includegraphics[width=.9\textwidth]{hardtable.pdf}}
  \caption{Mosaic Plot. On the vertical axis, the size of the boxes
    are determined by the fraction of the types of resources. On the
    horizontal axis the width of the boxes is proportional to the
    total counts, using the same bins as in
    Figure~\ref{fig:hardall}. Yellow boxes denote SPARQL Endpoints,
    green dataset descriptions, blue generic information resources and
    red vocabularies.}
  \label{fig:hardtable}
\end{figure}

@@

\begin{figure}[hb!]
  \centerline{%
    \includegraphics[width=.9\textwidth]{heuristictable.pdf}}
  \caption{Mosaic Plot for heuristic freshness lifetime. See caption
    of Figure~\ref{fig:hardtable} for description.  }
  \label{fig:heuristictable}
\end{figure}
